Do convolutional neural networks exhibit human-like attentional effects? Conflicting results from a visual search task

### 2019-05-28 docs/ccneuro2019/paper.tex
bullet-pointing intro in ccneuro/paper.tex

\section{Introduction}
\subsection{Attention}
Several attention mechanisms are currently used in machine learning 
and artificial intelligence to improve classification accuracy and similar 
metrics. Commonly used attention mechanisms consist essentially of weightings 
that are learned by updating the weights so as to minimize a loss function, 
with some additionally using recurrence
[@huSqueezeandExcitationNetworks2017; @vaswaniAttentionAllYou2017].
This understanding of attention as a mechanism to improve accuracy or other metrics 
stands in contrast to studies of attention in psychology and neuroscience. 
In these fields, theories of attention mechanisms are often built on 
results produced by experimental manipulations that impair behavior.
Perhaps the pre-eminent example of this approach to understanding attention is a 
a long-established form of visual search task [@wolfeVisualSearch1998]. In this behavioral
paradigm, subjects view a set of discrete items on a flat background and report whether a 
target is present or absent among distractors. Classically, results from this paradigm 
have been used to support different theories of \bf{selective covert visual attention}, 
a term that requires some defintion. The term "selective" is simply supposed to mean 
some mechanism that selects some visual inputs for further processing while necessarily 
discarding others. The word "covert" in this context means any mechanism that occurs 
"centrally", i.e. inside the brain, without overt orientation, i.e. without eye or head 
movements.
Our goal here is not to resolve the debate about whether selective covert visual 
attention is serial or parallel. Rather our goal is to better understand attention as 
defined in cognitive science and reconcile that with the definition used in artificial 
intelligence.

>>>>

\section{Introduction}
\subsection{Attention}
Multiple converging lines of evidence seem to suggest that training neural networks to 
perform tasks with human-like abilities causes them to acquire brain-like representations.

- If brain-like representations are both necessary and sufficient for human-like 
intelligence, then shouldn't the converse also be true? Shouldn't neural networks that 
have acquired brain-like representations behave like humans when asked to perform related 
tasks? We test this

In these fields, theories of attention mechanisms are often built on 
results produced by experimental manipulations that impair behavior.
Perhaps the pre-eminent example of this approach to understanding attention is a 
a long-established form of visual search task [@wolfeVisualSearch1998]. In this behavioral
paradigm, subjects view a set of discrete items on a flat background and report whether a 
target is present or absent among distractors. Classically, results from this paradigm 
have been used to support different theories of \bf{selective covert visual attention}, 
a term that requires some defintion. The term "selective" is simply supposed to mean 
some mechanism that selects some visual inputs for further processing while necessarily 
discarding others. The word "covert" in this context means any mechanism that occurs 
"centrally", i.e. inside the brain, without overt orientation, i.e. without eye or head 
movements.
- here we do not

Our goal here is not to resolve the debate about whether selective covert visual 
attention is serial or parallel. Rather our goal is to better understand attention as 
defined in cognitive science and reconcile that with the definition used in artificial 
intelligence.
